Intersection of non-matching grids of different dimensions

### 2016-09-29 paper_intersections.tex
Minor corrections in prolongations.

%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
  \label{fig:prolongation}
\end{figure}

The advancing front algorithm works the same way for both 1D and 2D components and is displayed in \fig{fig:prolongation}. The main idea is to compute intersections for a component element with all 
possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes in \fig{fig:prolongation}). We shall now describe the algorithm in detail.

On input we consider a candidate pair, for which a non-empty intersection is computed.
Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
Therefore, we iterate over the intersection points and further exploit their topological information.
There are 3 possible cases (applies both for 1D-3D and 2D-3D):
\begin{itemize}
    \item \textbf{IP lies on the component element side and inside the bulk element} \\
            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
            Next, we find the component neighboring elements over the sides and push all new candidate pairs
            [component neighbor -- current bulk element] into the component queue.
            Note, that there can be more than one neighbor on a side, if the component has branches.
    \item \textbf{IP lies on the component element side and on the surface of the bulk element} \\
            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
            push the following new candidate pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
            We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
\end{itemize}

>>>>

%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
  \caption{Advancing front algorithm for 1D-2D and 2D-3D intersections.}
  \label{fig:prolongation}
\end{figure}

The advancing front algorithm works the same way for both 1D and 2D components and is displayed by the scheme in \fig{fig:prolongation}. The main idea is to compute intersections for a component element with all 
possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes in \fig{fig:prolongation}). We shall now describe the algorithm in detail.

On input we consider a candidate pair, for which a non-empty intersection is computed.
Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
Therefore, we iterate over the intersection points and further exploit the topological information.
There are 3 possible cases (applies both for 1D-3D and 2D-3D), how the intersection might be prolonged:
\begin{itemize}
    \item \textbf{IP lies on the component element side and inside the bulk element} \\
            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
            Next, we find the component neighboring elements over the sides and push all new candidate pairs
            [component neighbor -- current bulk element] into the component queue.
            Note, that there can be more than one neighbor on a side, if the component has branches.
    \item \textbf{IP lies on the component element side and on the surface of the bulk element} \\
            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
            push the new candidate pairs [current component element -- bulk neighbor] into the bulk queue and [component neighbor -- bulk neighbor] into the component queue.
    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
            We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
\end{itemize}
